### 2016-03-10 ch05-initvals/initial-values.tex
Bode BK1613 in ch05 downsized

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/bode-bk1613.tikz}
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
  \label{fig:bk1613}
\end{figure}

@@

Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
First, the \gls{LPM} solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.

@@

\subsection{Implementation aspects}
This section discusses some implications and recommendations for the implementation of  a system identification toolbox.

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/bode-bk1613.tikz}
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

@@

Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2N_W + 1$ data points and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$ or $\bigO{N_W} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N N_W^3}$.

@@

\subsection{Implementation aspects}
This section presents some implications and recommendations for the implementation of  a system identification toolbox.
